---
title: "Second R Markdown for Midterm"
author: "Jing Qian"
date: "10/11/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1:  What is your current path?

```{bash}
pwd
```

## Question 2:  What is the date?

```{bash}
date
```

## Question 3:  Please make a new directory under the directory you are in called "mydirectory"

```{bash}
mkdir mydirectory
```

## Question 4:  What are the last 5 commands you have in your history

```{bash}
history 5
```


## Question 5:  Please put the following data into a file called "numbers.txt" using bash in R in a code block, where each number is on its own line using echo and the appropriate optional tag.

*1234
*12121
*3434
*123
*12341239879

```{r}
x <- c(1234, 12121, 3434, 123, 12341239879)
write.table(x, file = "numbers.txt")
```

## Question 6:  Please cat the file numbers.txt you just created

```{bash}
cat numbers.txt
```

## Question 7:  How many characters and how many lines are in the file?

```{bash}
wc -c numbers.txt  
wc -l numbers.txt  
wc -w numbers.txt  
```

## Question 8: Please create a sed command (e.g. sed 's/match/replace/g' numbers.txt) to commify the list of numbers in thousands place to the screen.  For example: 1,234 or 12,121

```{bash}
sed -e :a -e 's/\(.*[0-9]\)\([0-9]\{3\}\)/\1,\2/;ta' numbers.txt
```

## Question 9:  Please make the 'numbers.txt' file private such that only you can read and write it.  Nobody at the group level can read it, write or execute it.

```{bash}
chmod 700 numbers.text
```

## Question 10:   Please make that file 'numbers.txt' such that you can read and write to it, and everyone else on the computer both world and group can just read it.

```{bash}
chmod 744 numbers.text
```

## Question 11:  Please scrape or download the information behind the gene PTEN into a file from this [web-page](https://ghr.nlm.nih.gov/gene/PTEN)

```{bash}
wget https://ghr.nlm.nih.gov/gene/PTEN.pdf
```

## Question 12:  Please echo your PATH

```{bash}
echo $PATH
PATH = $PATH:/usr/local/bin
```

## Question 13:  Please add ~/bin to your existing path

```{bash}
export PATH=$PATH:/usr/local/bin
```

## Question 14:  Please find files ending in md in your current directory

```{bash}
find . -name "*.md"
```

## Question 15:  Please put all in the previous commands in your history into a file and call that file "history.txt"

```{bash}
cat .bash_history >> history.txt
```

## Question 16:  Please print the first 5 lines of your history by piping history into head

```{bash}
head 5 history.txt
```

## Question 17:  How would I specify to send me a reminder email every 8 minutes using a crontab?

```{bash}
8 * * * * echo 'Hello Dr.craig' | mail -s 'reminder' someone@example.com
```

## Question 18: What is the first line of a BASH script?

```{bash}
# !/bin/bash
```




<!-- The text below is just to reformat the page, using css styling -->
```{r results="asis", echo = FALSE}
cat("
<style>
h1 {
    background-color: #990000;
    color:#FFF;
    text-align:center;
}
h2 {
   background-color:#f3d6d6;
   text-align:center;
   color:#333
}
h3 {
   margin-left:-5px;
   color:#333
}

</style>
")
```
